---
title: "My dynamic report"
output: html_fragment
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
```

```{r}
library(tidyverse)

# Load and clean data
logged_data <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vS1aRljG5xmP2ObmFxf2b_L9CTceFbhCFk22WQyqkTV3HY7vjoozv1xw26QMsEMR3iMjd9xK72gBUnK/pub?output=csv")

latest_data <- logged_data %>%
  select(-Timestamp) %>%
  rename(video_length = How.long.was.the.video...to.the.nearest.minute.,
         subscribed = Are.you.subscribed.to.the.video.creator.,
         video_finished = Did.you.watch.the.entire.video.,
         genre = Which.genre.does.the.video.best.fit.)

# Create summary values for the first paragraph
total_count <- nrow(latest_data)

# Summary for Chart 1
report_summary_1 <- latest_data %>%
  group_by(video_finished) %>%
  summarise(mean_length = mean(video_length, na.rm = TRUE))

# Summary for Chart 2
report_sub_stats <- latest_data %>%
  group_by(subscribed) %>%
  summarise(
    total_vids = n(),
    finished_vids = sum(video_finished == "Yes"),
    completion_rate = (finished_vids / total_vids) * 100
  )
```

# Analysis of Video Consumption and Engagement
This report explores my personal media habits by analyzing video data collected via Google Sheets. The goal is to identify trends in video length, retention rate, and the impact of subscription status on completion rates. The data recorded through my form recorded the genre, length, whether I finished the video, and if I was subscribed to the creator for the last `r total_count` videos I watched.

```{r}
# Finding the mean video length of finished and unfinished videos
report_summary_1 <- latest_data %>%
  group_by(video_finished) %>%
  summarise(
    mean_length = mean(video_length, na.rm = TRUE)
  )

# Plotting the means found above
ggplot(report_summary_1, aes(x = video_finished, y = mean_length)) +
  geom_col(fill = "skyblue") +
  labs(
    title = "Average Video Length: Finished vs Not Finished",
    x = "Watched Entire Video",
    y = "Average Length (minutes)"
  )
```
## Video Completion by length
The plot above displays the average length of videos that were not watched in entirety versus those that were. The average length for videos I didn't finish is `r round(report_summary_1$mean_length[1], 1)` minutes, while the videos I did finish averaged `r round(report_summary_1$mean_length[2], 1)` minutes.

```{r}
# Ploting subscribed vs unsubscribed against whether videos are finished or not
ggplot(latest_data, aes(x = subscribed, fill = video_finished)) +
  geom_bar(position = "dodge") +
  labs(
    x = "Subscribed to Creator?",
    y = "Total Number of Videos",
    fill = "Finished Video"
  ) +
  theme_minimal()

# Calculating the corresponding percentages
report_sub_stats <- latest_data %>%
  group_by(subscribed) %>%
  summarise(
    total_vids = n(),
    finished_vids = sum(video_finished == "Yes"),
    completion_rate = (finished_vids / total_vids) * 100
  )

```
## The Impact of Subscription on Watch Behavior
Does being subscribed to a creator make me more likely to finish their content? The bar chart above compares the count of finished vs. unfinished videos based on subscription status. The percentage of videos finished as a nonsubscriber is `r report_sub_stats$completion_rate[1]` and the percentage of videos finished as a subscriber is `r report_sub_stats$completion_rate[2]`.
